Viscous Erosion in Porous Media

### 2018-03-04 docs/methods/erosion_methods.tex
NM

We point out that most exponential-integrator methods use some form of quadrature to treat \eqref{eq:mu}, but, here, we have simply applied the same RK2 method that is used for the rest of the system. We believe this to be a simple approach to arrive at a self-consistent discretization of desired accuracy because it avoids choices regarding which quadrature to use (midpoint, trapezoid, Simpson's etc.) and can be generalized to other time-stepping methods, such as fourth-order Runge-Kutta.

>>>>

We point out that most exponential integrators use some form of quadrature to treat \eqref{eq:mu}, but, here, we have simply applied the same RK2 method that is used for the rest of the system. We believe this to be a simple, systematic approach to arrive at a self-consistent discretization of desired accuracy because it avoids choices regarding which quadrature to use (midpoint, trapezoid, Simpson's, etc.) and can be easily generalized to other time-stepping methods, such as fourth-order Runge-Kutta.
